Hierarchical Dispatching and Overriding

### 2017-10-05 NewVersion/sections/Formalization.tex
refine S3 done

There are two typing rules for method invocation: \textsc{(T-Invk)} and \textsc{(T-PathInvk)}. \textsc{(T-Invk)} is the typing judgement for a normal method invocation, which is similar to Featherweight Java. It checks the type of the specific method, by using an auxiliary function \mbody. \mbody is the function for looking up methods, which we will illustrate later in Section~\ref{subsec:auxdefs}. After the method type is obtained, we check that arguments and the receiver have compatible types. \textsc{(T-PathInvk)} is the typing judgement for a path invocation. Besides the conditions of \textsc{(T-PathInvk)}, \textsc{(T-PathInvk)} requires the receiver to be the subtype of the specified
path type. 
% and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.

@@

Rule \textsc{(T-Intf)} defines the typing rule for interfaces. The
condition\bruno{Well, there are two conditions. I suggest you explain
  in a bit more detail the 2 conditions, since this rule seems to be
  the more complex one. Some examples may help.} \yanlin{controversial rule. lets discuss later} helps to ensure unambiguity and type soundness of the calculus. We will
introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not
ambiguous during runtime. Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime
in any case. The interface check is responsible for capturing ambiguity during compilation.

>>>>

There are two typing rules for method invocation: \textsc{(T-Invk)} and \textsc{(T-PathInvk)}. \textsc{(T-Invk)} is the typing judgement for a normal method invocation. First it ensures that the method receiver $e_0$ type checks to a type $I_0$. Then it checks the type of the specific method, by using an auxiliary function $\mbody(m, I_0, I_0)$, which is the function for looking up methods that we will illustrate in more detail in Section~\ref{subsec:auxdefs}. The form of \mbody is different to FJ, which has two parameters. The first $I_0$ represents the dynamic type and the second, the static type. If the result of \mbody is not \Undefined, it means the method exists and the corresponding method parameters and return types are given. After the method type is obtained, we check that all arguments $\overline{e}$ type check to $\overline{I}$ which are subtypes of $\overline{J}$. \textsc{(T-PathInvk)} is the typing judgement for a path invocation. Besides the conditions of \textsc{(T-Invk)}, \textsc{(T-PathInvk)} requires the type of receiver to be the subtype of the specified path type. 
% and \textsc{(T-SuperInvk)} checks if the enclosing type directly extends the specified super type.

@@

\bruno{Well, there are two conditions. I suggest you explain
  in a bit more detail the 2 conditions, since this rule seems to be
  the more complex one. Some examples may help.} \yanlin{controversial rule. lets discuss later} 
Rule \textsc{(T-Intf)} defines the typing rule for interfaces. Interface $I$ type checks only if the following conditions are satisfied: 1) all methods $\overline{M}$ that are directly defined in $I$ type check; 2) method lookup $\mbody(m, I, J)$ successes as long as the method $m$ is defined in any interface $J$ which is an ancestor of $I$; 3)if an original method $m$ defined in interfaces $I$ overrides another original method defined in an ancestor of $I$, then the method types are compatible. These conditions ensure unambiguity and type soundness of the calculus. We will introduce \mbody{} and some counter-examples later. But intuitively, if $\mbody(m,I,J)$ is defined, that means $\new{I}.J::m()$ is not ambiguous during runtime. Therefore the condition says that if an expression type checks, it should not introduce ambiguity during runtime in any case. The interface check is responsible for capturing ambiguity during compilation.
